Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-22 paper.tex
reply to todos

Before turning to the definition of the abstract data types, we first
give the definition of values used by the \effCEK{C}, as they are
mentioned in the definition of the ADTs.

\todo[inline]{The notation $\hcvOOinj{P}{v}$ is non-standard
   and should be explained. -JS}

\begin{definition}[Values for the \effCEK{C} machine] \label{def:values-effCEK}
  \[
  \begin{array}{rclr}
	\stxrule{v}{}{
		\hcvOOtt \mid
		\hcvOOfun{c}{\rho}{x}{e}{c} \mid
		\hcvOOcons{v}{c}{v}{c} \mid
		\hcvOOinl{v}{c} \mid
		\hcvOOinr{v}{c} \mid
		\hcvOOinj{P}{v}
	}
  \end{array}
  \]
\end{definition}

\todo[inline]{We also need to define results $r$ for \effCEK{C} -JS}

>>>>

Before turning to the definition of the abstract data types, we first
give the definition of values and cast results used by the \effCEK{C}, as they 
are mentioned in the definition of the ADTs.

\todo[inline]{The notation $\hcvOOinj{P}{v}$ is non-standard
   and should be explained. -JS
\\---\\
What is the standard way to display it? -KC}

\begin{definition}[Values and cast results for the \effCEK{C} machine] 
\label{def:values-effCEK}
  \[
  \begin{array}{rclr}
	\stxrule{v}{values}{
		\hcvOOtt \mid
		\hcvOOfun{c}{\rho}{x}{e}{c} \mid
		\hcvOOcons{v}{c}{v}{c} \mid
		\hcvOOinl{v}{c} \mid
		\hcvOOinr{v}{c} \mid
		\hcvOOinj{P}{v}
	}
\stxrule{r}{cast results}{
	\rOOsucc{v} \mid
	\rOOfail{l}
}
  \end{array}
  \]
\end{definition}

\todo[inline]{We also need to define results $r$ for \effCEK{C} -JS
\\---\\
Fixed. -KC}
